The LBRY Trending Algorithm

### 2021-11-18 tex/ms.tex
Figure

If an LBC change occurs, the update is instead
\begin{align}
Y_{t+1} &= kY_t + M(\ell_t, \ell_{t+1}), \label{eqn:decay_with_spike}
\end{align}
where the second term is the `mass' of a `trending spike', and depends on
the old and new LBC values. A simple idea is to set the mass of the trending
spike equal to the change in LBC:
\begin{align}
M(\ell_t, \ell_{t+1}) &= \ell_{t+1} - \ell_t.
\end{align}
However, in practice this simple choice might lead to undesirable results.
Many supports on the LBRY network are created by publishers themselves,
attempting to boost their own content's visibility. If an item receives
many organic views and a moderate number of small tips, one might expect it
to trend, yet with the linear choice for $M$, it will have no hope of
competing with a `whale' who can deposit 100,000 LBC in support without
blinking an eye. In Section~\ref{sec:spike_mass}, we simulate several
different patterns of support, and choose a function $M$ such that
the size of trending spikes makes `minnows' able to compete with `whales',
at least to a greater extent than they can with the linear choice.

>>>>

If an LBC change occurs, the update is instead
\begin{align}
Y_{t+1} &= kY_t + M(\ell_t, \ell_{t+1}), \label{eqn:decay_with_spike}
\end{align}
where the second term is the `mass' of a `trending spike', and depends on
the old and new LBC values. A simple idea is to set the mass of the trending
spike equal to the change in LBC:
\begin{align}
M(\ell_t, \ell_{t+1}) &= \ell_{t+1} - \ell_t.
\end{align}
For a claim created at height $t=50$ with 1 LBC staked towards it, and then
later supported with 3 more LBC at height $t=550$, the trending score
would respond as in Figure~\ref{fig:simple}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/simple.pdf}
\caption{An example of how the trending score might vary over time
for a single claim.\label{fig:simple}}
\end{figure}

However, in practice this simple choice might lead to undesirable results.
Many supports on the LBRY network are created by publishers themselves,
attempting to boost their own content's visibility. If an item receives
many organic views and a moderate number of small tips, one might expect it
to trend, yet with the linear choice for $M$, it will have no hope of
competing with a `whale' who can deposit 100,000 LBC in support without
blinking an eye. In Section~\ref{sec:spike_mass}, we simulate several
different patterns of support, and choose a function $M$ such that
the size of trending spikes makes `minnows' able to compete with `whales',
at least to a greater extent than they can with the linear choice.
